Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-09-20 paper/paper.Rmd

The APIs, the scripts used to access them, and the resulting data set are contained in the supplementary materials, available at [https://github.com/mvparrot/face-recognition](https://github.com/mvparrot/face-recognition). The APIs evaluated were:

>>>>

The APIs, the scripts used to access them, and the resulting data set are contained in the supplementary materials, available at [https://github.com/mvparrot/face-recognition/paper](https://github.com/mvparrot/face-recognition/paper). The APIs evaluated were:
